---
title: "Regex"
author: "Runzi Qi"
date: "2022/2/2"
output: html_document
---
This program is written by RicardoQi on February 2nd, 2022 as R-egex assignment. The code applies both dplyr() and stringr() to help organize data. 
```{r}
library(dplyr)
library(stringr)
```
The data set is loaded.
```{r}
#Read the csv file
MData<- read.csv("C:\\Users\\qi199\\Documents\\R-eproducibility\\InputData\\measurements.csv")
```
Then, the dplyr() function is used to organize the order of columns and create a new column named Sp.
```{r}
#Mutate the data to create a new column named Sp
MData <- MData %>%
  mutate(Sp = Organism)
```
Next, the former Organism column is divided into two parts, and the first half is abbreviated using sub().
```{r}
#Converting the first half of species name
g <- sub("(^.)", "\\1.", MData$Sp)
g <- word(g, 1, sep = fixed(' '))
g <- str_sub(g, start=1, end=2)
```
Another half of the name is separated, but the contents are unchanged.
```{r}
#Obtain the other half of name
f <- sub("(^.)", "\\1.", MData$Sp)
f <- word(f, 2, sep = fixed(' '))
```
The two parts of newly-synthesized Sp is concatenated using paste(). 
```{r}
#Concatenate two variables together to obtain final names
MData$Sp <- paste(g,f)
```
The Sp column is moved to the first column to replace the Organism column, then the latter is removed. 
```{r}
#Moving Sp column to the first and generate the table
MData1 <- MData %>%
  select(Sp, everything())
  select(MData1, -2)
```
The csv file output is saved.
```{r}
#Export the csv file
write.csv(MData1, "C:\\Users\\qi199\\Documents\\R-eproducibility\\Output\\MeasShort.csv" )
```

  
  
```

